### 2025-07-02 machine-learning.qmd
20250702 - standardized regression coefficients

```{r}
library("petersenlab")
library("parallel")
library("future")
library("missRanger")
library("powerjoin")
library("tidymodels")
library("LongituRF")
library("gpboost")
library("tidyverse")
```

@@

@@

# Define Model
ridge_spec <- 
  parnsnip::linear_reg(
    penalty = tune::tune(),
    mixture = 0) %>%
  parsnip::set_engine("glmnet")

>>>>

```{r}
library("petersenlab")
library("parallel")
library("future")
library("missRanger")
library("powerjoin")
library("tidymodels")
library("LongituRF")
library("gpboost")
library("effectsize")
library("tidyverse")
```

@@

final_model %>%
  workflows::extract_fit_parsnip() %>% 
  effectsize::standardize_parameters()

@@

# Define Model
ridge_spec <- 
  parsnip::linear_reg(
    penalty = tune::tune(),
    mixture = 0) %>%
  parsnip::set_engine("glmnet")
